Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2016-09-30 article/article_for_submission.tex
Little typo
Laurent last changes before advisors review

In \cite[Sec. 4.2]{HicJim} it is shown that for any $f\in\cc$,
\begin{equation}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}_{\mathfrak{C}(m)}=\epsilon_{I}, \label{errbd}
\end{equation}
where one may increase $m$ until the error bound $\epsilon_{I}$ is small enough.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$.
\begin{figure}[!ht]
\caption{Given the true value of $I_1$, the figure shows in blue the region of all possible values of $\underline{S}_u(\vI)$. There, $\underline{S}_u^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)}$ and $\underline{S}_u^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)}$.}
\centering
\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

@@

For the two test functions, results of the three variants are compared based on the true estimation errors. These errors correspond to the absolute difference between the true values and their estimates:
$$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
We also compare the total number of evaluations of each variant. Results are averaged over $r=100$ repetitions using Owen's scrambled Sobol' sequences \cite{HonHic00a,Owe95}. For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points). The algorithm error bound factor is set to $\mathfrak{C}(m)=10\times 2^{-m}$.

@@

Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. 
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and averaged total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0003$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0010$ & $0$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0038$ & $0.25$    \\ \hline
 $x_5$ & $0.0015$ & $0.0024$ & $0$  \\ \hline
 $x_6$ & $0.0015$ & $0.0026$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.bratley.B}
\end{table}
The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$. Failure rates are similar to those of Variant $A.b$. Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring much improvement for this example.
\bigskip

@@

The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$. If $\vect{Y}\sim N(\vzero,I_d)$, given a matrix $M$ such that $\mathsf{\Sigma}=MM^t$, then $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$. Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$. Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$.

Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$.

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.a$ with Cholesky decomposition.}
\centering
\begin{tabular}{ccccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
 $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
 $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
 $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
 $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
 $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
 $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
\end{tabular}
\label{res.AsianChol.Aa}
\end{table}

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.b$ with Cholesky decomposition.}
\centering
\begin{tabular}{ccccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
 $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
 $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
 $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
 $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
 $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
 $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
\end{tabular}
\label{res.AsianChol.Ab}
\end{table}

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and number of evaluations of Variant $B$ with Cholesky decomposition.}
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
 $x_1$ & $0.2120$ & $131072$ \\ \hline
 $x_2$ & $0.1350$ & $129766$ \\ \hline
 $x_3$ & $0.0774$ & $62290$ \\ \hline
 $x_4$ & $0.0338$ & $49961$ \\ \hline
 $x_5$ & $0.0149$ & $48845$ \\ \hline
 $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
\end{tabular}
\label{res.AsianChol.B}
\end{table}

Variant $A.b$ is the best because the total number of evaluations.................

@@

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.b$ with PCA decomposition.}
\centering
\begin{tabular}{ccccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
 $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
 $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
 $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
 $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
 $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
 $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
\end{tabular}
\label{res.AsianPCA.Ab}
\end{table}

One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.

@@

The sequential estimation procedure proposed in this article offers a practical solution with the construction of an estimator and error bound for Sobol' indices. The number of points is progressively augmented until the error bound becomes lower than a user specified tolerance. The procedure presented combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices. Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods. The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions and a real case model. The variant combining Saltelli's strategy and ``Correlation 2'' gave the best results with low failure rates across all indices.

>>>>

In \cite[Sec. 4.2]{HicJim} it is shown that for any $f\in\cc$,
\begin{equation}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
\end{equation}
where one may increase $m$ until the error bound $\epsilon_{I}$ is small enough.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$ given the true value of $I_1$.
\begin{figure}[!ht]
\caption{Given the true value of $I_1$, the figure shows in blue the region of all possible values of $\underline{S}_u(\vI)$. There, $\underline{S}_u^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)}$ and $\underline{S}_u^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)}$.}
\centering
\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.pdf}
\label{fig:1}       % Give a unique label
\end{figure}

@@

For the two test functions, results of the three variants are compared based on the true estimation errors. These errors correspond to the absolute difference between the true values and their estimates:
$$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
We also compare the total number of evaluations of each variant. Results are averaged over $100$ repetitions using Owen's scrambled Sobol' sequences \cite{HonHic00a,Owe95}. For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points). The algorithm error bound factor is set to $\mathfrak{C}(m)=10\times 2^{-m}$.

@@

Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. 
\begin{table}[!ht]
\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
\centering
\begin{tabular}{cccc}
\hline
 input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
 $x_1$ & $0.6529$ &  $0.0003$ & $0$ \\ \hline
 $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
 $x_3$ & $0.0370$ &  $0.0010$ & $0$ \\ \hline
 $x_4$ & $0.0133$ &  $0.0038$ & $0.25$    \\ \hline
 $x_5$ & $0.0015$ & $0.0024$ & $0$  \\ \hline
 $x_6$ & $0.0015$ & $0.0026$ & $0$  \\ \hline \hline
\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
\end{tabular}
\label{res.bratley.B}
\end{table}
The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$. Failure rates are similar to those of Variant $A.b$. Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring much improvement for this example.
\bigskip

@@

The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$. If $\vect{Y}\sim N(\vzero,I_d)$, given a matrix $M$ such that $\mathsf{\Sigma}=MM^t$, then $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$. Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$. Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$. We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions. The tolerance $\varepsilon$ and parameters $\ell^*$, $r$ and $\mathfrak{C}(m)$ are set as previously.

Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
\centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.2120$ & $0.5650$  \\ \hline
 $x_2$ & $0.1370$ & $0.4420$  \\ \hline
 $x_3$ & $0.0820$ & $0.3150$  \\ \hline
 $x_4$ & $0.0408$ & $0.1950$  \\ \hline
 $x_5$ & $0.0142$ & $0.0944$  \\ \hline
 $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
\end{tabular}
\label{res.AsianChol.Aa}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
 \centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
 $x_1$ & $0.2120$ & $0.5650$  \\ \hline
 $x_2$ & $0.1370$ & $0.4420$ \\ \hline
 $x_3$ & $0.0822$ & $0.3150$  \\ \hline
 $x_4$ & $0.0434$ & $0.1950$  \\ \hline
 $x_5$ & $0.0169$ & $0.0944$  \\ \hline
 $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
\end{tabular}
\label{res.AsianChol.Ab}
\end{table}
\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
%\centering
%\begin{tabular}{ccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.2120$ & $131072$ \\ \hline
% $x_2$ & $0.1350$ & $129766$ \\ \hline
% $x_3$ & $0.0774$ & $62290$ \\ \hline
% $x_4$ & $0.0338$ & $49961$ \\ \hline
% $x_5$ & $0.0149$ & $48845$ \\ \hline
% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
 \centering
\begin{tabular}{cc}
\hline
 input & $\widehat{\underline{S}}_u$ \\ \hline
 $x_1$ & $0.2120$ \\ \hline
 $x_2$ & $0.1350$ \\ \hline
 $x_3$ & $0.0774$ \\ \hline
 $x_4$ & $0.0338$ \\ \hline
 $x_5$ & $0.0149$ \\ \hline
 $x_6$ & $0.0028$ \\ \hline \hline
\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
\end{tabular}
\label{res.AsianChol.B}
\end{table}
It turns out that Variant $A.b$ does not better than Variant $A.a$. Averaged Sobol' estimates are similar while the averaged number of model evaluations is slightly worse. The explanation is that total effect Sobol' indices require more evaluations than their corresponding first-order indices. As such, ``Correlation 2'' falls into case 1) explained in Section \ref{sec:4.2}. Variant $B$ shows a drastic improvement on the total number of evaluations with the drawback of a false estimation for input $x_4$. Indeed, the discrepancy is higher than $\epsilon$ when comparing with the other two variants.

@@

\begin{table}[!ht]
\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
%\centering
%\begin{tabular}{ccccc}
%\hline
% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
 \centering
\begin{tabular}{ccc}
\hline
 input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
 $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
 $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
 $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
 $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
 $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
 $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
\end{tabular}
\label{res.AsianPCA.Ab}
\end{table}
One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.

@@

The sequential estimation procedure proposed in this article offers a practical solution with the construction of an estimator and error bound for Sobol' indices. The number of points is progressively augmented until the error bound becomes lower than a user specified tolerance. The procedure presented combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices. Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods. The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions. Overall, the variant combining Saltelli's strategy and ``Correlation 2'' gave the best results, with low failure rates across all indices.
